### 2019-06-05 2-Chapters/3-Chapter/chapter3.tex
Changed \paragraph{XXX} to \paragraph{XXX.}
Starting to conclude Ch2

\paragraph{Simulation loop}
%
Any simulation library targeting single-player bandit problems must implement at least three components:
reward distributions, MAB algorithm, and a simulation loop that essentially looks like this:
\begin{itemize}
    \item First, initialize the MAB problem and one or more algorithms,
    \item Then, for $t=1$ to $t=T$ (known before hand), repeat the following block (for each algorithm). Ask algorithm $\cA$ her chosen arm $A(t)$, then sample a (random) reward $r(t)$ (\iid) from distribution $\nu_{A(t)}$, and finally feeds the observation $(A(t), r(t))$ to the algorithm,
    \item At the end, compute the cumulated reward, the regret, plot visualizations etc.
\end{itemize}
%
Note that the second step is repeated a large number of times (\eg, $N=100$), in order to study \emph{mean} regret and not only the regret in one single trajectory.
If one wants to compare algorithms on a same problem, it is possible to sample all the rewards $(r_k(t))_{k\in[K], t\in[T]}$ before-hand, and store them so that for each repetition of the simulation, the randomness from the environment (\ie, the rewards) has the same impact on all the algorithms.

\paragraph{Simulation loop for multi-player bandit}

@@

gaussian_problem = MAB({'arm_type': Gaussian, 'params': means})
gaussian_problem.plotHistogram()  # display the histogram showed below
    \end{minted}
    \caption{Example of Python code to create Bernoulli and Gaussian arms, a MAB problem with $K=3$ arms, a plot a histogram of rewards, with SMPyBandits}
    % \captionof{listing}{Example of Python code to create Bernoulli and Gaussian arms, a MAB problem with $K=3$ arms, a plot a histogram of rewards, with SMPyBandits. \label{lst:3:pythonCodeCreateProblem}}
    \label{lst:3:pythonCodeCreateProblem}
\end{listing}
\end{small}

@@

SMPyBandits is a complete open-source implementation of single-player (classical) bandit algorithms,
containing over 65 algorithms (in the module \texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.html}{Policies}}).
It uses a well-designed hierarchical structure and class inheritance scheme (as detailed on the various UML diagrams showed on the \texttt{\href{https://SMPyBandits.GitHub.io/uml_diagrams/README.html}{uml\_diagrams}} folder) to minimize redundancy in the codebase.
For instance, most existing algorithms are index-based, and new ones can be written easily by inheriting from the \texttt{IndexPolicy} class (\texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.IndexPolicy.html}{Policies.IndexPolicy}}).
An index-based algorithm computes an index $I_k(t)\in\mathbb{R}$ for each arm $k$ at time $t$ and simply play $A(t) = \arg\max_k I_k(t)$.
For instance the code specific to the UCB algorithm \cite{LaiRobbins85,Auer02} is as short as this (and fully documented):

@@

% \paragraph{List of algorithms}

@@

\paragraph{Two different problems}

@@

\paragraph{Other parameters of the experiments}

@@

% \paragraph{Mean regret}

@@

% \paragraph{Computation time}

@@

% \paragraph{Storage cost}

@@

\paragraph{Interpretation}

@@

\paragraph{Bash command to run these experiments}

>>>>

\paragraph{Simulation loop.}
%
Any simulation library targeting single-player bandit problems must implement at least three components:
reward distributions, MAB algorithm, and a simulation loop that essentially looks like this:
\begin{itemize}
    \item First, initialize the MAB problem and one or more algorithms,
    \item Then, for $t=1$ to $t=T$ (known before hand), repeat the following block (for each algorithm). Ask algorithm $\cA$ her chosen arm $A(t)$, then sample a (random) reward $r(t)$ (\iid) from distribution $\nu_{A(t)}$, and finally feeds the observation $(A(t), r(t))$ to the algorithm,
    \item At the end, compute the cumulated reward, the regret, plot visualizations etc.
\end{itemize}
%
Note that the second step is repeated a large number of times (\eg, $N=100$), in order to study \emph{mean} regret and not only the regret in one single trajectory.
If one wants to compare algorithms on a same problem, it is possible to sample all the rewards $(r_k(t))_{k\in[K], t\in[T]}$ before-hand, and store them so that for each repetition of the simulation, the randomness from the environment (\ie, the rewards) has the same impact on all the algorithms.

\paragraph{Simulation loop for multi-player bandit.}

@@

gaussian_problem = MAB({'arm_type': Gaussian, 'params': means})
gaussian_problem.plotHistogram()  # display the histogram shown below
    \end{minted}
    \caption{Example of Python code to create Bernoulli and Gaussian arms, a MAB problem with $K=3$ arms, a plot a histogram of rewards, with SMPyBandits}
    % \captionof{listing}{Example of Python code to create Bernoulli and Gaussian arms, a MAB problem with $K=3$ arms, a plot a histogram of rewards, with SMPyBandits. \label{lst:3:pythonCodeCreateProblem}}
    \label{lst:3:pythonCodeCreateProblem}
\end{listing}
\end{small}

@@

SMPyBandits is a complete open-source implementation of single-player (classical) bandit algorithms,
containing over 65 algorithms (in the module \texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.html}{Policies}}).
It uses a well-designed hierarchical structure and class inheritance scheme (as detailed on the various UML diagrams shown on the \texttt{\href{https://SMPyBandits.GitHub.io/uml_diagrams/README.html}{uml\_diagrams}} folder) to minimize redundancy in the codebase.
For instance, most existing algorithms are index-based, and new ones can be written easily by inheriting from the \texttt{IndexPolicy} class (\texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.IndexPolicy.html}{Policies.IndexPolicy}}).
An index-based algorithm computes an index $I_k(t)\in\mathbb{R}$ for each arm $k$ at time $t$ and simply play $A(t) = \arg\max_k I_k(t)$.
For instance the code specific to the UCB algorithm \cite{LaiRobbins85,Auer02} is as short as this (and fully documented):

@@

% \paragraph{List of algorithms.}

@@

\paragraph{Two different problems.}

@@

\paragraph{Other parameters of the experiments.}

@@

% \paragraph{Mean regret.}

@@

% \paragraph{Computation time.}

@@

% \paragraph{Storage cost.}

@@

\paragraph{Interpretation.}

@@

\paragraph{Bash command to run these experiments.}
